First I would like to thank my husband, Ryan, for his patience and encouragements throughout my time in graduate school.  Without his support, this would have never been possible.

I would like to thank my advisor, Harry Barrett, for providing me with an opportunity to work on a very interesting project.  This dissertation would not have been possible without his guidance and his tremendous knowledge in the field.  I would like to express my gratitude to Lars Furenlid, for his help with many hardware challenges and providing much professional advice as well.  I would like to thank Eric Clarkson for patiently answering my numerous math questions.

I would also like to thank Mike Arthur for showing me how to use the tools in the machine shop and Hans Roehrig allowing me to use his x-ray lab and equipment for all of my experiments.

I would also like to express my sincere thanks for all of my lab mates, Vaibhav Bora, Cecile Carlson, Esen Salcin, Joseph Ortiz, Jin Park, and Joy Ding.  They have provided an incredible friendly environment and many interesting conversations throughout my time here.  I would also like to express my gratitude to Merry Warner and Liz Hague for helping me place lots of orders and giving a lot of support throughout the years.  I would like to thank Christy Barber for putting up with me while we were office mates.

I am grateful for the funding I have received.  I have received support from Biomedical Imaging and Spectroscopy (BMIS) program, Achievement Reward for College Scientists (ARCS) scholarship, and NIH grants T32 EB000809, P41 EB002035, and R01 EB000803.